---
title: "Eval Static Analysis"
author: "Chakshu Goyal"
date: "07/06/2018"
output:
  html_document: default
  pdf_document: default
---

## 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
library(tools)
#knitr::kable(head(arrange(evalCntPerPkg, desc(freq)) , 20) , col.names = c("Package" , "Number of evals"))
#knitr::kable(head(arrange(outlyingRows, desc(freq)) , 5) , col.names = c("Package" , "Number of evals"))
#lineCountPerPkg <- 
#  lineCountPerFile %>%
#    group_by(pkg) %>%
#      summarise(lineCount = sum(lineCount), charCount = sum(charCount))
#lineNdEvalCountPerPkg <- merge(lineCountPerPkg, evalCntPerPkg)
#evalCntPerPkgLeft <- evalCntPerPkg[ !(evalCntPerPkg$pkg %in% lineCountPerPkg$pkg) , ]
#evalCntPerPkgLeft
```

## Load the data
Usage of the function eval in R-packages.
To get evals.csv, run - Rscript evalCrawler.R /mnt/nvme0/R/CRAN-extracted
```{r}
evaldf <- read_csv("evals.csv")
```

## Plot occurences of evals in packages
```{r}
ggplot(evaldf , aes(pkg)) + 
  geom_bar() + 
  theme(axis.text.x = element_blank()) + 
  labs(y="Number of evals", x="packages", title="Figurative distribution of the usage of eval in various packages")
```

Top 20 packages using eval
```{r}
evalCntPerPkg <- dplyr::count(evaldf, pkg)
knitr::kable(
  evalCntPerPkg %>%
  top_n(20, wt=n) %>%
  arrange(desc(n)))
```

Eval distribution in packages - density and histogram plots
```{r}
ggplot(evalCntPerPkg, aes(n)) + 
  geom_density()+ scale_x_log10() + 
  labs(y="Number of projects (density)", x="Number of Evals - (log scaled)", title="Evals distribution in the packages")
ggplot(evalCntPerPkg , aes(n)) + 
  geom_histogram(bins=50) + 
  scale_x_log10() + 
  labs(y="Number of projects", x="Number of Evals", title="Evals distribution in the packages - histogram")
```

Exploring outliers
```{r}
ggplot(evalCntPerPkg , aes(x = "" , y = n)) +
  geom_boxplot() +
  labs(y="Number of Evals", x="Packages", title="Evals distribution in the packages - boxplot")
```

```{r}
outlyingVals <- boxplot.stats(evalCntPerPkg$n)$out
outlyingRows <- filter(evalCntPerPkg, n %in% outlyingVals)
evalCountPerFile <- dplyr::count(evaldf, path)
```

Top Outliers
```{r}
##top outliers
knitr::kable(
  evalCountPerFile %>% 
    top_n(5, wt=n) %>% 
    arrange(desc(n)))
```

Bottom Outliers
```{r}
knitr::kable(
  evalCountPerFile %>% 
    top_n(5, wt=n) %>% 
    arrange(n))
#knitr::kable(head(arrange(outlyingRows, n) , 5) , col.names = c("Package" , "Number of evals"))
```

Plotting without outliers
```{r}
evalCntPerPkgMod <- evalCntPerPkg[ !(evalCntPerPkg$n %in% outlyingVals), ]
ggplot(evalCntPerPkgMod , aes(x = "" , y = n)) +
  geom_boxplot() +
  labs(y="Number of Evals", x="Packages", title="Evals distribution in the packages - boxplot (outliers removed)")
```

##Some interesting plots 

```{r}
knitr::kable(tribble(
  ~A,~B,
  "Total Number of eval occurences combined" , nrow(evaldf),
  "Total Number of packages considered" , "12574",  #the latter is from the output of the evalCrawler.R script
  "Number of packages using eval" , nrow(unique.data.frame(evaldf["pkg"]))
))
```

Distribution as per usage
```{r}
# Eval occurences per use
knitr::kable(dplyr::count(evaldf , use) , col.names = c("Usage" , "Frequency"))
```

Files using most evals
```{r}
evalCountPerFile %>% 
  top_n(10, wt=n) %>% 
  arrange(desc(n)) %>% 
  knitr::kable()
```

Plot number of evals vs number of chars in files
```{r}
charCountPerFile <- 
  evaldf %>%
  group_by(path) %>%
  summarise(lineCount = first(lineCount), charCount = first(charCount), pkg = first(pkg))
charNdEvalCountPerFile <- merge(charCountPerFile , evalCountPerFile)

ggplot(data = charNdEvalCountPerFile, mapping = aes(x = charCount, y = n)) + 
  geom_point() + 
  labs(y="Number of Evals", x="Number of chars", title="Eval usage per char in files")
```

Plot number of evals vs number of lines in pkgs
```{r}
slocdf <- read_csv("sloc.csv")
lineCountPerPkg <-
  slocdf %>%
  filter(language == "R") %>%
  select(pkg = package , code)
lineNdEvalPerPkg <- merge( evalCntPerPkg , lineCountPerPkg , all = FALSE)
ggplot(data = lineNdEvalPerPkg, mapping = aes(x = code, y = n)) +
  geom_point() +
  labs(y="Number of Evals", x="Number of lines", title="Eval usage per lines in packages")
ggplot(data = filter(lineNdEvalPerPkg , n < 1000), mapping = aes(x = code, y = n)) +
  geom_point() +
  labs(y="Number of Evals", x="Number of lines", title="Eval usage per lines in packages (with less than 1000 evals)")
```

## Eval occurences in folders inside of packages
```{r}
evaldf <- 
  evaldf %>% 
  rowwise() %>% 
  mutate(folder = strsplit(path, split="/")[[1]][7] ,extension = file_ext(path)  )
evalCntPerFolder <- dplyr::count(evaldf , folder)

knitr::kable(head(arrange(evalCntPerFolder, desc(n)) , 20) , col.names = c("Folder" , "Number of evals"))
ggplot(evalCntPerFolder , aes(n)) + 
  geom_histogram(bins=50) + 
  scale_x_log10() + 
  labs(y="Number of Folders", x="Number of Evals", title="Evals distribution in the folders - histogram")

evalCntPerExtension <- dplyr::count(evaldf , extension)
knitr::kable(head(arrange(evalCntPerExtension, desc(n)) , 10) , col.names = c("File Extension  " , "Number of evals"))
```
